---
title: "Results"
output: pdf_document
---


```{r}
#load your data here


library(knitr)
library(xtable)
library(venn)
library(gridExtra)
library(ggplot2)
prezRez<-function(mat){
	apply(mat,1,function(s){
		paste0(ifelse(s[4]==0,"\\textbf{",""),
			sprintf("%0.2f",s[1])," [",sprintf("%0.2f",s[2]),"; ",sprintf("%0.2f",s[3]),"]",
			ifelse(s[4]==0,"}","")
			)
	})
}
```

# Proportion of each type of toxicity (in column) co-occurring with an other type of toxicity (in
row) 

```{r}
#insert here the names of the columns of the 5 types of toxicity
nams<-c("gradeC","gradeD","gradeH","gradeG","gradeO")
tmp<-matrix("",5,5)
for(i in 1:5){
	for(j in 1:5){
		tmp[i,j]<-ifelse(i==j,"-",sprintf("%0.2f",sum(data[,nams[i]]>0 & data[,nams[j]]>0)/sum(data[,nams[j]]>0)))
	}
}
rownames(tmp)<-colnames(tmp)<-c("Cutaneous","Digestive","General disorder","Hematologic","Others")
kable(tmp,format="latex",align=c("l","r","r","r","r","r"))
```

# Number of toxicities by type and grade

```{r}
tmp<-matrix(NA,4,5)
for(i in 1:5){
	counts<-as.numeric(table(data[,nams[i]])[-1])
	tmp[,i]<-c(counts,sum(counts))
}
tmp<-cbind(c(1,2,"$\\geq$ 3","Total"),tmp,apply(tmp,1,sum))
for(i in 2:ncol(tmp)) tmp[,i]<-sapply(tmp[,i],function(vec) if(nchar(vec)<=3){return(vec)}else{return(paste0(substr(vec,1,nchar(vec)-3),",",substr(vec,nchar(vec)-2,nchar(vec))))})
colnames(tmp)<-c("Grade","Cutaneous","Digestive","General disorder","Hematologic","Others","Total")
print(xtable(tmp,align=c("l","l","r","r","r","r","r","r")),include.rownames=F,sanitize.text.function=force)
```

# Co-occurence of the toxicity (all grades) for all reported cycles.

```{r}
x<-list(Cutaneous=which(data[,nams[1]]>0),
	G=which(data[,nams[2]]>0),
	Digestive=which(data[,nams[3]]>0),
	Hematologic=which(data[,nams[4]]>0),
	Others=which(data[,nams[5]]>0)
	)
names(x)<-c(paste0("Cutaneous\n(n=",sum(data[,nams[1]]>0),")"),
	paste0("General disorders (n=",sum(data[,nams[2]]>0),")"),
	paste0("Digestive\n(n=",sum(data[,nams[3]]>0),")"),
	paste0("Hematologic\n(n=",sum(data[,nams[4]]>0),")"),
	paste0("Others\n(n=",sum(data[,nams[5]]>0),")"))
venn(x,zcol = c("red", "palegreen", "blue","yellow","purple","orange","cyan"))

```

# Models fit

```{r}
load("results/CRModel.RData")
load("results/POModel.RData")
```

## Continuation ratio model

### Parameter estimates

```{r}
b0<-summary(fit0)$summary[grep("betaFx",rownames(summary(fit0)$summary)),colnames(summary(fit0)$summary)%in%c("mean","2.5%","97.5%")]
b0<-cbind(b0,I(b0[,2]<=0 & b0[,3]>=0))
rez<-cbind(sort(apply(expand.grid(c("Cutaneous","Digestive","General","Hemato","Other"),c("a1","a2","a3","Dose1","Dose2","Dose3","Time1","Time2","Time3"),stringsAsFactors=F),1,function(x) paste(x,collapse="_"))),prezRez(b0),b0[,4])
rez[,3]<-c("*","")[1*I(as.numeric(b0[,2])<=0 & as.numeric(b0[,3])>=0)+1]
colnames(rez)<-c("parameter","value","signif")
rez2<-as.data.frame(rez[grep("Cutaneous",rez[,1]),-ncol(rez)],stringsAsFactors=F)
colnames(rez2)<-c("parameter","Cutaneous")
for(i in c("Digestive","General","Hemato","Other")){
	rez2<-within(rez2,assign(i,rez[grep(i,rez[,1]),2]))
}
rez2$parameter<-c("Intercept$_{\\textnormal{Grade}\\geq 1}$","Intercept$_{\\textnormal{Grade}\\geq 2}$","Intercept$_{\\textnormal{Grade}\\geq 3}$",
	"Dose$_{\\textnormal{Grade}\\geq 1}$","Dose$_{\\textnormal{Grade}\\geq 2}$","Dose$_{\\textnormal{Grade}\\geq 3}$",
	"Cycle$_{\\textnormal{Grade}\\geq 1}$","Cycle$_{\\textnormal{Grade}\\geq 2}$","Cycle$_{\\textnormal{Grade}\\geq 3}$")
print(xtable(rez2,align=c("l","l","r","r","r","r","r")),include.rownames=F,sanitize.text.function=force)

```

### Random effect correlation matrix

```{r}
tmp<-summary(fit0)$summary[grep("Omega",rownames(summary(fit0)$summary)),]
tmp<-paste0(sprintf("%.2f",tmp[,1])," [",sprintf("%.2f",tmp[,4]),"; ",sprintf("%.2f",tmp[,8]),"]")
b<-matrix(tmp,5,5)
rownames(b)<-colnames(b)<-c("Cutaneous","Digestive","General disorder","Hematologic","Others")
diag(b)<-1
b[upper.tri(b)]<-""
kable(b,format="latex",align=c("l","r","r","r","r","r"))

```

### Posterior predictive distribution

Observed (empty circle) vs expected probability of each type of toxicity at each cycle according to the CR model. The median expected probability (filled circles) and the 95% prediction interval were obtained from 1,000 simulations from the posterior predictive distribution of the model.

```{r}
tmp<-predDist(fitCR)
files<-c("cut","dig","gd","hem","oth")
nams<-c("Cutaneous","Digestive","General disorder","Hematologic","Others")
for(k in 1:dim(obsProbs)[3]){
	i<-2
	dat<-data.frame(Toxicity=nams[k],Grade="Grade >= 1",Cycle=1:6,Median=apply(expProbs[,i,,k],1,median),
		pQmin=apply(expProbs[,i,,k],1,function(x) quantile(x,probs=0.025,na.rm=T)),
		pQmax=apply(expProbs[,i,,k],1,function(x) quantile(x,probs=0.975,na.rm=T)))
	obs<-data.frame(Toxicity=nams[k],Grade="Grade >= 1",Cycle=1:6,Observed=obsProbs[,i,k])
	for(i in 3:dim(obsProbs)[2]){
		dat<-rbind(dat,data.frame(Toxicity=nams[k],Grade=paste0("Grade >= ",i-1),Cycle=1:6,
			Median=apply(expProbs[,i,,k],1,median),
			pQmin=apply(expProbs[,i,,k],1,function(x) quantile(x,probs=0.025,na.rm=T)),
			pQmax=apply(expProbs[,i,,k],1,function(x) quantile(x,probs=0.975,na.rm=T))))
		obs<-rbind(obs,data.frame(Toxicity=nams[k],Grade=paste0("Grade >= ",i-1),Cycle=1:6,Observed=obsProbs[,i,k]))
	}
	assign(files[k],{
		ggplot(dat, aes(y=Median,x=Cycle,colour=Grade))+
		geom_point(data=obs,mapping=aes(x=Cycle,y=Observed,colour=Grade),size=2.5,shape=21,fill="white",show.legend = FALSE)+
		geom_errorbar(aes(ymin=pQmin, ymax=pQmax), width=.1)+
		geom_point() +ylim(0, 0.75) + ylab("Probability") + xlab("Cycle") + ggtitle(paste0(nams[k]," toxicities"))
	})
}
legend<-get_legend(cut)
for(f in files){assign(f,get(f)+theme(legend.position="none"))}
grid.arrange(cut,dig,gd,hem,oth,legend,ncol=3,nrow=2)

```

### WAIC

WAIC $=$ `r WAIC(fitCR)$waic`




## Proportional odds model

### Parameter estimates

```{r}
b0<-summary(fit0)$summary[grep("betaFx",rownames(summary(fit0)$summary)),colnames(summary(fit0)$summary)%in%c("mean","2.5%","97.5%")]
b0<-cbind(b0,I(b0[,2]<=0 & b0[,3]>=0))
rez<-cbind(sort(apply(expand.grid(c("Cutaneous","Digestive","General","Hemato","Other"),c("a1","a2","a3","Dose1","Time1"),stringsAsFactors=F),1,function(x) paste(x,collapse="_"))),prezRez(b0),b0[,4])
rez[,3]<-c("*","")[1*I(as.numeric(b0[,2])<=0 & as.numeric(b0[,3])>=0)+1]
colnames(rez)<-c("parameter","value","signif")
rez2<-as.data.frame(rez[grep("Cutaneous",rez[,1]),-ncol(rez)],stringsAsFactors=F)
colnames(rez2)<-c("parameter","Cutaneous")
for(i in c("Digestive","General","Hemato","Other")){
	rez2<-within(rez2,assign(i,rez[grep(i,rez[,1]),2]))
}
rez2$parameter<-c("Intercept$_{\\textnormal{Grade}\\geq 1}$","Intercept$_{\\textnormal{Grade}\\geq 2}$","Intercept$_{\\textnormal{Grade}\\geq 3}$","Dose","Cycle")
print(xtable(rez2,align=c("l","l","r","r","r","r","r")),include.rownames=F,sanitize.text.function=force)

```

### Random effect correlation matrix

```{r}
tmp<-summary(fit0)$summary[grep("Omega",rownames(summary(fit0)$summary)),]
tmp<-paste0(sprintf("%.2f",tmp[,1])," [",sprintf("%.2f",tmp[,4]),"; ",sprintf("%.2f",tmp[,8]),"]")
b<-matrix(tmp,5,5)
rownames(b)<-colnames(b)<-c("Cutaneous","Digestive","General disorder","Hematologic","Others")
diag(b)<-1
b[upper.tri(b)]<-""
kable(b,format="latex",align=c("l","r","r","r","r","r"))

```


### Posterior predictive distribution

Observed (empty circle) vs expected probability of each type of toxicity at each cycle according to the PO model. The median expected probability (filled circles) and the 95% prediction interval were obtained from 1,000 simulations from the posterior predictive distribution of the model.


```{r}
tmp<-predDist(fitPO)
files<-c("cut","dig","gd","hem","oth")
nams<-c("Cutaneous","Digestive","General disorder","Hematologic","Others")
for(k in 1:dim(obsProbs)[3]){
	i<-2
	dat<-data.frame(Toxicity=nams[k],Grade="Grade >= 1",Cycle=1:6,Median=apply(expProbs[,i,,k],1,median),
		pQmin=apply(expProbs[,i,,k],1,function(x) quantile(x,probs=0.025)),
		pQmax=apply(expProbs[,i,,k],1,function(x) quantile(x,probs=0.975)))
	obs<-data.frame(Toxicity=nams[k],Grade="Grade >= 1",Cycle=1:6,Observed=obsProbs[,i,k])
	for(i in 3:dim(obsProbs)[2]){
		dat<-rbind(dat,data.frame(Toxicity=nams[k],Grade=paste0("Grade >= ",i-1),Cycle=1:6,
			Median=apply(expProbs[,i,,k],1,median),
			pQmin=apply(expProbs[,i,,k],1,function(x) quantile(x,probs=0.025)),
			pQmax=apply(expProbs[,i,,k],1,function(x) quantile(x,probs=0.975))))
		obs<-rbind(obs,data.frame(Toxicity=nams[k],Grade=paste0("Grade >= ",i-1),Cycle=1:6,Observed=obsProbs[,i,k]))
	}
	assign(files[k],{
		ggplot(dat, aes(y=Median,x=Cycle,colour=Grade))+
		geom_point(data=obs,mapping=aes(x=Cycle,y=Observed,colour=Grade),size=2.5,shape=21,fill="white",show.legend = FALSE)+
		geom_errorbar(aes(ymin=pQmin, ymax=pQmax), width=.1)+
		geom_point() +ylim(0, 0.75) + ylab("Probability") + xlab("Cycle") + ggtitle(paste0(nams[k]," toxicities"))
	})
}
legend<-get_legend(cut)
for(f in files){assign(f,get(f)+theme(legend.position="none"))}
grid.arrange(cut,dig,gd,hem,oth,legend,ncol=3,nrow=2)

```



### WAIC

WAIC $=$ `r WAIC(fitPO)$waic`

